---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# nhgCI

<!-- badges: start -->
<!-- badges: end -->

The **nhgCI** package provides methods for constructing exact and approximate confidence intervals for the parameters of the Negative Hypergeometric distribution.

It supports the following methods:

- Analog to Clopper-Pearson

- Conditional Minimal Cardinality (CMC)

- Crow & Gardner (CG)

- Blaker

The package handles cases where either:
- The number of successes (`M`) is unknown, or
- The total population size (`N`) is unknown.

## Installation

You can install the development version from GitHub with:

```r
# install.packages("devtools")
devtools::install_github("rroggenk/nhgCI")
```


## Example

Here's a basic example of using `nhgCI`:

```{r example, eval = FALSE}
library(nhgCI)

# Confidence intervals for unknown M
nhgCI_M(N = 30, m = 5, conf_level = 0.95, method = "Analog to Clopper-Pearson")

# Confidence intervals for unknown N
nhgCI_N(M = 10, m = 5, conf_level = 0.95, method = "CMC")
```

## Notes

- For `nhgCI_M()`, confidence intervals are computed for all appropriate values of observed failures `x` automatically.
- For `nhgCI_N()`, the number of observed failures `x` is theoretically unbounded.  
  You may need to increase the `max_N` parameter if your desired `x` value does not appear.

Some computations (especially for large sample sizes or high precision) may take a while to complete.

